Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-29 paper/paper.tex
update authors

\author{Lianna Hoag}
\email{jonquill.howlett@colostate.edu} %update email 
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}

\author{Shea Spalding}
\email{jonquill.howlett@colostate.edu} %update email 
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}

\renewcommand{\shortauthors}{Howlett, Hoag, Spalding} %I don't know how to format this for three authors 
% the template does not show any shortauthors

@@

@@

\subsection[short]{Apparatus}
Apparatus

>>>>

\author{Shea Spalding}
\email{Shea.Spalding@colostate.edu} %update email 
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80525-0650} %chktex 8 %the rest of the zip will need to be corrected
}

\renewcommand{\shortauthors}{Howlett, Spalding} %I don't know how to format this for three authors 
% the template does not show any shortauthors

@@

% Put the related works here
% \section{Related Works}

@@

\subsection[short]{Apparatus}
Apparatus
\subsubsection{EyeWriter 2.0}
\subsubsection{QB Test}
\subsubsection{Typing Test}

I will add typing methodology here.
